---
title: "utm_latlong"
author: "Paul Apivat Hanvongse"
date: "6/25/2020"
always_allow_html: yes
output: 
        html_document: default
        pdf_document: default
keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages and Libraries

```{r, echo=TRUE}
library(maps)
library(tidyverse)
library(sp)
library(rmarkdown)
```

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

## World and Thai Maps

First, we'll use `map_data` function from `ggplot2` to turn any map from the `maps` package into a data frame. This provides longitude and lattitude data. Then, we'll filter for Thailand to get Thai longtitude and lattitude data. 


```{r, echo=TRUE}
world.map <- map_data("world")
head(world.map)

THAI.map <- world.map %>% filter(region=='Thailand')
head(THAI.map)
```

## Longitude and Lattitude Value Ranges

Before converting UTM to longitude/lattitude data, we should know the range of both Longitudes and Lattitudes for Thailand.

```{r, echo=TRUE}
summary(THAI.map$long)
summary(THAI.map$lat)
```

## Jobpost Data Frame

Our objective is to visualize utm_x and utm_y in the `jobpost` data frame by turning them into lattitude and longitude data first. The `jobpost` data frame is retrieved from PostgreSQL. 

Preparation includes writing it to CSV before loading into Rmarkdown.

```{r, echo=TRUE}
jobpost <- read.csv("jobpost.csv")
glimpse(jobpost)
```

## Subset Data Frame called UTM

We'll select only `utm_x` and `utm_y` columns from `jobpost` because we're interested in these two columns. 

```{r, echo=TRUE}
utm <- data.frame(jobpost$utm_x, jobpost$utm_y)
str(utm)
```

## Handle Missing Values and Outliers

Row 50 in `jobpost` and also `utm` is missing so we'll delete that. Then we'll also delete row 11 because it's location is Zambia, Africa and its longitude and lattitude numbers are very different from Thailand - which will *distort* the map. 

```{r, echo=TRUE}
utm <- utm[-50,]
utm <- utm[-11,]
jobpost <- jobpost[-50,]
jobpost <- jobpost[-11,]
str(utm)
str(jobpost)
```

## Conversion of UTM into Lat/Long

After some research, we find out that Thailand's UTM zone is 47N. The stack overflow source I used to find the conversion code is [here](https://stackoverflow.com/questions/30018098/how-to-convert-utm-coordinates-to-lat-and-long-in-r/30018607). 

We'll create two SpatialPoints object classes. Then transform them into a data frame containing lat and long data. 

Remember to load `sp` library for this operation. 

```{r, echo=TRUE}
sputm <- SpatialPoints(utm, proj4string=CRS("+proj=utm +zone=47N +datum=WGS84"))  
spgeo <- spTransform(sputm, CRS("+proj=longlat +datum=WGS84")) 

thai.map2 <- data.frame(Location = jobpost$location, lat = spgeo$jobpost.utm_y, long = spgeo$jobpost.utm_x)

head(thai.map2)
```

## Visualize with GGPLOT2

Here we'll visualize the `THAI.map` we created previously and overlay the new Lat/Long data points (from UTM).

We can see a concentration of `utm` data points from `jobpost` were made in Bangkok and the greater Bangkok areas with some jobs also posted outside Bangkok. 


```{r, echo=TRUE}
THAI.map %>% ggplot() + geom_map(map = THAI.map, aes(x=long, y=lat, map_id = region), fill='white', color='black') + geom_point(data = thai.map2, aes(x=long, y=lat, color="red", alpha = .9))

```


