---
title: "utm_latlong"
author: "Paul Apivat Hanvongse"
date: "6/25/2020"
always_allow_html: yes
output: 
        html_document: default
        pdf_document: default
keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages and Libraries

```{r, echo=TRUE}
library(maps)
library(tidyverse)
library(sp)
library(rmarkdown)
```

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

## World and Thai Maps

First, we'll use `map_data` function from `ggplot2` to turn any map from the `maps` package into a data frame. This provides longitude and lattitude data. Then, we'll filter for Thailand to get Thai longtitude and lattitude data. 


```{r, echo=TRUE}
world.map <- map_data("world")
head(world.map)

THAI.map <- world.map %>% filter(region=='Thailand')
head(THAI.map)
```

## Jobposts

Our objective is to visualize utm_x and utm_y in the `jobpost` data frame by turning them into lattitude and longitude data first. The `jobpost` data frame is retrieved from PostgreSQL. 

```{r, echo=TRUE}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
